SVG: The Paper

### 2022-04-19 Analysis/index.Rmd
removing old plots

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```

@@

ggplot(d, aes(x, y, colour = condition)) + geom_point(alpha = 0.25) +
  #coord_cartesian(xlim = c(0, 1), ylim = c(0, 1)) + 
  facet_wrap(~observer)

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y)) %>%
  ggplot(aes(x, y, colour = condition)) + geom_point(alpha = 0.25) #+
#coord_cartesian(xlim = c(0, 1), ylim = c(0, 1))

plt_x <- ggplot(d, aes(x)) + geom_histogram(bins = 10) 
plt_y <- ggplot(d, aes(y)) + geom_histogram(bins =  8) 
plt_x + plt_y
```

>>>>

ggplot(d, aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()
```

```{r fig.cap="Distirbution of median intial selection."}

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()

@@
